---
title: "TopicAnalysis"
author: "lushi"
date: "07/05/2019"
output: html_document
---

```{r setup, include=FALSE}
require(data.table)
require(fastDummies)
library(psych)
```

## R Markdown

This script compare the LIWC score in each level

```{r, include FALSE}
#path = '/Users/lucia/phd_work/Clpsy'
path = '/home/lucia/phd_work/shareTask/'
setwd(path)
#labels <- read.csv("./data/clpsych19_training_data/crowd_train.csv")
post <- read.csv("./data/clpsych19_training_data/Btrain.csv")
SW <- read.csv("./data/clpsych19_training_data/Btrain_NoNoise_SW_LIWC.csv")
AllLiwc <- read.csv("./data/clpsych19_training_data/BtrainLiwc.csv")
# for class A, we need to filter out posts that talk about self 
allLabel <- read.csv("./data/clpsych19_training_data/crowd_train.csv")

```


now we compare the LIWC in SW posts
```{r pressure, echo=FALSE}

#AllLiwc$raw_label[is.na(AllLiwc$raw_label)]  <- 0

SW  <-SW[, c(7:100)]



getCompareStats <- function(results){
  group1  <- results[which(results$raw_label == 'a'), ] 
  group2  <- results[which(results$raw_label == 'b'), ] 
  group3  <- results[which(results$raw_label == 'c'), ] 
  group4  <- results[which(results$raw_label == 'd'), ] 
  #group5  <- results[which(results$raw_label == ''), ] 
  
  
  getSummary <- function(group){
    g1 <- psych::describe(group, quant=c(.25,.75))
    setDT(g1, keep.rownames = TRUE)[]
    gc1 <- g1[,c('rn', 'median', 'Q0.25', 'Q0.75')]
  
  return (gc1)
  }
  
  gc1 <- getSummary(group1)
  gc2 <- getSummary(group2)
  gc3 <- getSummary(group3)
  gc4 <- getSummary(group4)
  #gc5 <- getSummary(group5)
  
  
  LatextTable <- function(StartCol, endCol){
    summaryRe <- cbind(gc1[,c(1,2)], gc2[,StartCol:endCol])
    summaryRe <- cbind(summaryRe, gc3[,StartCol:endCol])
    summaryRe <- cbind(summaryRe, gc4[,StartCol:endCol])
   # summaryRe <- cbind(summaryRe, gc5[,StartCol:endCol])
    summaryRe2 <- format(summaryRe, digits = 2)
    
  }
  
  summaryResult <- LatextTable(2,2)
  return (summaryResult)
}


summaryResult <- getCompareStats(SW)

```

#LIWC comparison in SW posts 
```{r}
stargazer(summaryResult, type = 'text')

```

now we look at the top100 topics in all the users posts, divide the topics into groups and compute the topic counts 
```{r, include = FALSE}
NoSW <- subset(post, post$subreddit != 'SuicideWatch')
Top100 <- data.frame(table(NoSW$subreddit))
Top100<- Top100[order(-Top100$Freq),]
Top100 <- Top100[1:100, ]

#count topic
groups <- post[,c('user_id','raw_label')]
#number of people in each group
groups2 <- groups[!duplicated(groups$user_id),]
NumP <- data.frame(table(groups2$raw_label))

GetThemeCount <- function(theme, themeName, bootstrapN){
  post$themeCount<- ifelse(post$subreddit == theme , 1, 0)
  # aggregate theme count on user level
   Seltheme <- post[post$themeCount == 1,]
  themes <- data.frame(table(Seltheme$user_id))
  colnames(themes) <- c('user_id', themeName)
  groupTheme <- merge(themes, groups, by = 'user_id', all.x = T)
  themes <- data.frame(table(groupTheme$raw_label))
  themes$NumPeople <- NumP$Freq
  themes$Freq <- themes$Freq/NumP$Freq
  return(themes)
}

GetThemePost <- function(theme, themeName){
  post$themeCount<- ifelse(post$subreddit == theme , 1, 0)
  # aggregate theme count on user level
  Seltheme <- post[post$themeCount == 1,]
  return (Seltheme)
}
```


```{r, include=FALSE}
GetTopicCor <- function(theme, themeName, bootstrapN){
  #generate a df for correlation
  GetDf<- function(theme, themeName){
    post$themeCount<- ifelse(post$subreddit == theme, 1, 0)
    # aggregate theme count on user level
    Seltheme <- post[post$themeCount == 1,]
    themes <- data.frame(table(Seltheme$user_id))
    colnames(themes) <- c('user_id', themeName)
    groupTheme <- merge(themes, groups, by = 'user_id', all.x = T)
    groupTheme <- groupTheme[!duplicated(groupTheme$user_id),]
    groupTheme$raw_label <- as.character(groupTheme$raw_label)
    groupTheme$raw_label[groupTheme$raw_label==""] <- 'NRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'a'] <- 'LRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'b'] <- 'MoRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'c'] <- 'HRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'd'] <- 'VHRisk'
    
    return(groupTheme)
  }
  
  #convert category to dummy vari then do correlation
  GetThemeCor <- function(groupTheme){
    # #permutation (sample the order of the data)
    # #set.seed(42)
    groupDum <- fastDummies::dummy_cols(groupTheme$raw_label)
    groupDumPer <- groupDum[sample(nrow(groupDum)),]
    corRe <- cor(groupDumPer[,-1], groupTheme[,2])
    return(corRe)
  }

  #permutation, times: number of iteration, theme:subreddit, get the most frequent value as result
  getMedian <- function(RiskLevel){
    NRisk <- c()
    for(i in 1:bootstrapN){
      groupTheme <- GetDf(theme, themeName)
      CorRe <- GetThemeCor(groupTheme)
      NRisk[[i]] <- round(CorRe[RiskLevel], digits = 2)
      mostFreq <- data.frame(sort(table(NRisk),decreasing=TRUE))
      mostFreq[,1] <- as.numeric(as.character(mostFreq[,1]))
      result <- mostFreq[1,1]
    }
    return (result)
  }
  
  NRisk <- getMedian(1)
  LRisk <- getMedian(2)
  VHRisk <- getMedian(3)
  MoRisk <- getMedian(4)
  HRisk <- getMedian(5)
  
  RiskCor <- data.frame(c(NRisk,LRisk,VHRisk,MoRisk,HRisk))
  RiskCor$rn <- c('NRisk','LRisk','VHRisk','MoRisk','HRisk')
  return(RiskCor)
}

#get topic correlation with risk level
l = Top100$Var1

l = c('gaming','aww')

GetAllCor <- function(topics, boostrapN){
  preCor = NULL
  mergeDf = NULL
  for (topic in topics){
    if (is.null(preCor) == F){
      CorRe <- GetTopicCor(topic, 'topic', boostrapN)
      colnames(CorRe) <- c(topic,'rn')
      mergeDf <- merge(preCor, CorRe, by ='rn', all= T)
      preCor <- mergeDf
    }
    else{
      CorRe <- GetTopicCor(topic, 'topic', boostrapN)
      colnames(CorRe) <- c(topic,'rn')
      preCor <- CorRe
    }
  }
  return(mergeDf)
  
}

system.time(allCor <- GetAllCor(l, 100))

#now we create the latex table
allCorLat <- data.frame(t(allCor))
allCorLat <- allCorLat[rowSums(is.na(allCorLat)) != ncol(allCorLat), ]
allCorLat <- allCorLat[,-6]
allCorLat[is.na(allCorLat)] <- 0
colnames(allCorLat) = allCorLat[1, ] # the first row will be the header
allCorLat <- allCorLat[-1, ]
colnames(allCorLat) <- c("data_HRisk","data_LRisk","data_MoRisk", "data_NRisk",  "data_VHRisk")

#convert to Latex table
ConvertNum <- function(df){
  for (i in colnames(df)){
    df[,c(i)] <- as.numeric(as.character(df[,c(i)]))
  }
  return (df)
}

allCorLat2 <- ConvertNum(allCorLat)
allCorLat2 <- data.frame(sapply(allCorLat2, roundup))
setDT(allCorLat, keep.rownames = TRUE)[]
allCorLat2$subreddit<- allCorLat$rn

#stargazer(allCorLat2, type = 'latex',  summary=FALSE, out='/Users/lucia/phd_work/Clpsy/data/clpsych19_training_data/allCorLat2.csv', out.header=FALSE)

library(XLConnect)
writeWorksheetToFile("/Users/lucia/phd_work/Clpsy/data/clpsych19_training_data/allCorLat2.xlsx", 
                 data = allCorLat2, 
                 sheet = "cor", 
                 header = TRUE,
                 clearSheets = TRUE)

```

#get 95% confidence interval 
```{r}
GetConfi <- function(theme, themeName, bootstrapN){
  GetDf<- function(theme, themeName){
    post$themeCount<- ifelse(post$subreddit == theme, 1, 0)
    # aggregate theme count on user level
    Seltheme <- post[post$themeCount == 1,]
    themes <- data.frame(table(Seltheme$user_id))
    colnames(themes) <- c('user_id', themeName)
    groupTheme <- merge(themes, groups, by = 'user_id', all.x = T)
    groupTheme <- groupTheme[!duplicated(groupTheme$user_id),]
    groupTheme$raw_label <- as.character(groupTheme$raw_label)
    groupTheme$raw_label[groupTheme$raw_label==""] <- 'NRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'a'] <- 'LRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'b'] <- 'MoRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'c'] <- 'HRisk'
    groupTheme$raw_label[groupTheme$raw_label== 'd'] <- 'VHRisk'
    
    return(groupTheme)
  }
  
  
  GetThemeCor <- function(groupTheme){
    # #permutation (sample the order of the data)
    #set.seed(42)
    groupDum <- fastDummies::dummy_cols(groupTheme$raw_label)
    groupDumPer <- groupDum[sample(nrow(groupDum)),]
    corRe <- cor(groupDumPer[,-1], groupTheme[,2])
    return(corRe)
  }

  #permutation, times: number of iteration, theme:subreddit, get the most frequent value as result
   getLeft <- function(RiskLevel){
    NRisk <- c()
    for(i in 1:bootstrapN){
      groupTheme <- GetDf(theme, themeName)
      CorRe <- GetThemeCor(groupTheme)
      NRisk[[i]] <- round(CorRe[RiskLevel], digits = 2)
      Freq <- data.frame(sort(table(NRisk),decreasing=TRUE))
      Freq[,1] <- as.numeric(as.character(Freq[,1]))
      meanR <- mean(as.numeric(as.character(Freq$Freq)))
      sdR <- sd(as.numeric(as.character(Freq$Freq)))
      n <- length(Freq$Freq)
      error <- qt(0.975,df=n-1)*sdR/sqrt(n)
      left <- round(meanR-error, digits = 0)
      leftBound <- data.frame(Freq[Freq$Freq == left, ])
      leftB <- leftBound$NRisk[1]
      
    }
    return (leftB)
   }
  #  
   getRight <- function(RiskLevel){
    NRisk <- c()
    for(i in 1:bootstrapN){
      groupTheme <- GetDf(theme, themeName)
      CorRe <- GetThemeCor(groupTheme)
      NRisk[[i]] <- round(CorRe[RiskLevel], digits = 2)
      Freq <- data.frame(sort(table(NRisk),decreasing=TRUE))
      Freq[,1] <- as.numeric(as.character(Freq[,1]))
      meanR <- mean(as.numeric(as.character(Freq$Freq)))
      sdR <- sd(as.numeric(as.character(Freq$Freq)))
      n <- length(Freq$Freq)
      error <- qt(0.975,df=n-1)*sdR/sqrt(n)
      right <- round(meanR+error, digits = 0)
      rightBound <- data.frame(Freq[Freq$Freq == right, ])
      rightB <- rightBound$NRisk[1]

    }
    return (rightB)
  }

   leftNRisk <- getLeft(1)
   rightNRisk<- getRight(1)
# 
   leftLRisk <- getLeft(2)
   rightLRisk<- getRight(2)

   leftVHRisk <- getLeft(3)
   rightVHRisk<- getRight(3)
  #
   leftMoRisk <- getLeft(4)
   rightMoRisk<- getRight(4)

   leftHRisk <- getLeft(5)
   rightHRisk<- getRight(5)
  #
  RiskCorConfi <- data.frame(c(leftNRisk,leftLRisk,leftVHRisk,leftMoRisk,leftHRisk))
  RiskCorConfi$Right <- data.frame(c(rightNRisk,rightLRisk,rightVHRisk,rightMoRisk,rightHRisk))
  RiskCorConfi$rn <- c('NRisk','LRisk','VHRisk','MoRisk','HRisk')

  names(RiskCorConfi) <- c('left','right','rn')
  return(RiskCorConfi)
}

ConfidenceInte <- GetConfi('aww','aww', 100)



```


here we compare the LIWC in selected themes, are the redditors of various risk level consistent in their psychological expressions across topics?
```{r}


getCompareStats2 <- function(results){
    group1  <- results[which(results$raw_label == 'a'), ] 
    group2  <- results[which(results$raw_label == 'b'), ] 
    group3  <- results[which(results$raw_label == 'c'), ] 
    group4  <- results[which(results$raw_label == 'd'), ] 
    group5  <- results[which(results$raw_label == ''), ] 
    
    
  getSummary <- function(group){
    g1 <- psych::describe(group, quant=c(.25,.75))
    g1$mean <- as.numeric(as.character(g1$mean))
    setDT(g1, keep.rownames = TRUE)[]
    gc <- g1[,c('rn', 'mean', 'Q0.25', 'Q0.75')]
    gc$mean<- round(gc$mean, digits = 2)
  
    return (gc)
  }
  
  gc1 <- getSummary(group1)
  gc2 <- getSummary(group2)
  gc3 <- getSummary(group3)
  gc4 <- getSummary(group4)
  gc5 <- getSummary(group5)
  
  
  LatextTable <- function(StartCol, endCol){
    summaryRe <- cbind(gc1[,c(1,2)], gc2[,StartCol:endCol])
    summaryRe <- cbind(summaryRe, gc3[,StartCol:endCol])
    summaryRe <- cbind(summaryRe, gc4[,StartCol:endCol])
    summaryRe <- cbind(summaryRe, gc5[,StartCol:endCol])
    #summaryRe2 <- format(summaryRe, digits = 2)
    
  }
  
  summaryResult <- LatextTable(2,2)
  return (summaryResult)
}

getStatTable <- function(theme, themeName){
  selPost <- GetThemePost(theme, themeName)
  themePostLIWC <- subset(AllLiwc, (AllLiwc$post_id %in% selPost$post_id))
  themePostLIWC  <- themePostLIWC[, c(7:100)]
  summaryThemeRe <- getCompareStats2(themePostLIWC)
  return(summaryThemeRe)
}

#the majority of posts in the fun theme are media, therefore, no LIWC scores
fun <- c('funny', 'aww')
funRe <- getStatTable(fun, 'fun')
funCount <- GetThemeCount(fun, 'fun')

#the number of mental health posts is a lot less, thus NA
mentalH <- c('depression', 'schizophrenia', 'selfharm')
mentalHRe <- getStatTable(mentalH, 'mentalH')
mentalHC <- GetThemeCount(mentalH, 'mentalH')



woman<- c('AskWomen','BabyBumps','TwoXChromosomes')
womanRe <- getStatTable(woman, 'woman')
womanC <- GetThemeCor(woman, 'woman')


womanC <- GetThemeCount(woman, 'woman')

game <- c('gaming', 'leagueoflegends', 'Fireteams', 'SteamGameSwap','hcfactions','summonerschool','Minecraft', 'pcmasterrace','amiibo','GlobalOffensiveTrade',	'pokemon','DotA2','starcraft','AnimalCrossing','GlobalOffensive','runescape','zelda','hearthstone','buildapc')
gameRe <- getStatTable(game, 'game')
gameC <- GetThemeCor(game, 'game')

infoShare <- c('askscience','todayilearned','technology','Android','techsupport','tipofmytongue','IAmA',
               'casualiama','Permaculture','motorcycles','guns','investing','business','MakeupAddiction',
               'poker','malefashionadvice','seedstock','breakingmom')

infoShareRe <- getStatTable(infoShare, 'infoShare')

GetThemeCount <- function(theme, themeName){
  post$themeCount<- ifelse(post$subreddit == theme , 1, 0)
  # aggregate theme count on user level
  Seltheme <- post[post$themeCount == 1,]
  themes <- data.frame(table(Seltheme$user_id))
  colnames(themes) <- c('user_id', themeName)
  groupTheme <- merge(themes, groups, by = 'user_id', all.x = T)
  themes <- data.frame(table(groupTheme$raw_label))
  themes$NumPeople <- NumP$Freq
  themes$Freq <- themes$Freq/NumP$Freq
  return(themes)
}

infoShareC <- GetThemeCount(infoShare, 'infoShare')
infoShareCor <- GetThemeCor(infoShare, 'infoShare')

```













