---
title: "featureCluster"
author: "lushi"
date: "14/03/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cluster)  # we'll use these packages
library(fpc)
library(mclust)
library(tidyverse)
library(fastDummies)
```


## Cluster Frequency and motivation feature 

```{r }
#setwd('/home/lucia/phd_work/shareTask/')
#setwd('/Users/lucia/phd_work/Clpsy')
FreqFea <- read.csv("/Users/lucia/phd_work/Clpsy/suicideDetection/features/FreqFea.csv")
moti <-  read.csv("/Users/lucia/phd_work/Clpsy/suicideDetection/features/motivations2.csv")
labels <- read.csv("/Users/lucia/phd_work/Clpsy/data/clpsych19_training_data/crowd_train.csv")

FreqFeaS <- FreqFea[, c(2,7,12:15)]
motiS <- moti[, c(2:9)]

FreqFeaL <- merge(labels, FreqFeaS, by ='user_id', all.y = T)
FreqFeaL<- merge(FreqFeaL, moti, by ='user_id', all.y = T)
FreqFeaL <-  FreqFeaL[,-8]  
freq <- FreqFeaL[3:14]

```

#get gower distance
```{r }
getGower <- function(data, binaryCol) {
  g.dist <-  daisy(data, metric="gower", type=list(asymm = binaryCol))
  print(summary(g.dist))
  return (g.dist)    
}



```


#mclust
```{r mclust}
getMclust <- function (gowerMatrix, clusterN){
  BIC <- mclustBIC(as.matrix(gowerMatrix))
  plot(BIC)
  mod1 <- Mclust(as.matrix(gowerMatrix), x = BIC, G= clusterN)
  #print(table(FreqFeaL$raw_label, mod1$classification))
  return (mod1$classification)
}

```

# adding sentiment feature 
```{r adding sentiment feature}
getUsertopicSent <- function(Topicfile, useridFile){
  topicSent <- read.csv(Topicfile)
  getid <- read.csv(useridFile)
  getid <- getid[,c('user_id', 'post_id')]
  topicSent <- merge(topicSent, getid, by = 'post_id', all.x = T)
  topicSentMean <- aggregate(topicSent[, 3:5], list(topicSent$user_id), mean)
  colnames(topicSentMean)[1] <- "user_id"
  return (topicSentMean)
}

useridFile <- "/Users/lucia/phd_work/Clpsy/data/clpsych19_training_data/BtrainNoNoiseSWStress.csv"
topicSentMean <- getUsertopicSent("/Users/lucia/phd_work/Clpsy/suicideDetection/features/topicSentiment.csv", useridFile)
#write.csv(topicSentMean, "/Users/lucia/phd_work/Clpsy/suicideDetection/features/UsertopicSentiment.csv")

topicSentMean2 <- getUsertopicSent("/Users/lucia/phd_work/Clpsy/suicideDetection/features/topicSentiment2.csv", useridFile)
write.csv(topicSentMean2, "/Users/lucia/phd_work/Clpsy/suicideDetection/features/UsertopicSentiment2.csv")

```

topicSentMean has stronger correlation with labels than topicSentMean2 but topicSentMean helps clustering better results
```{r }
sentimentProfile <- read.csv('/Users/lucia/phd_work/Clpsy/suicideDetection/features/users_sentiment_profile.csv')
freqSent <- merge(FreqFeaL, topicSentMean, by = 'user_id')
freqSent <- merge(freqSent, sentimentProfile, by = 'user_id', all.x=T)
freqSent$raw_label<-dplyr::recode(freqSent$raw_label,'a'=1,'b'=2,'c'=3,'d'=4)
freqSent <- fastDummies::dummy_cols(freqSent, select_columns = "raw_label")
freqSent$raw_label<- as.numeric(freqSent$raw_label)
cor(freqSent)

```

# remove features correlation with labels < 0.10
```{r}

freqSent2 <- subset(freqSent, select=-c(family_senti, sentiment, SWWordCount))
freqSentC <- freqSent2[3:15]
g.dist <- getGower(freqSentC, c(4, 5:10))
clusters <- getMclust(g.dist, 5)
cor(clusters, freqSent$raw_label)

#save cluster result in feature and merge features for training set
FreqFeaT<- merge(FreqFea, moti, by ='user_id', all.y = T)
FreqFeaT <-  FreqFeaT[,c(-2,-16)]  
FreqFeaT <- merge(FreqFeaT, topicSentMean, by = 'user_id')
FreqFeaT <- merge(FreqFeaT, labels, by = 'user_id')
FreqFeaT <- merge(FreqFeaT, sentimentProfile, by = 'user_id', all.x=T)

FreqFeaT$mclust <- clusters
write.csv(FreqFeaT, '/Users/lucia/phd_work/Clpsy/suicideDetection/features/FreqSentiMotiTopiFea.csv')



```


#merge test set 

get sentiment from test data
```{r }
useridFile <- "/Users/lucia/phd_work/Clpsy/data/clpsych19_training_data/testSWstressed.csv"
topicSentMean2T <- getUsertopicSent("/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/topicSentiment2.csv", useridFile)
write.csv(topicSentMean2T, "/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/UsertopicSentiment2.csv")

topicSentMeanT <- getUsertopicSent("/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/topicSentiment.csv", useridFile)
write.csv(topicSentMean2T, "/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/UsertopicSentiment.csv")
```

cluster with frequency, motivation and topic sentiment feature
```{r }

FreqFeaTe <- read.csv("/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/FreqFea.csv")
motiTe <-  read.csv("/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/motivations2.csv")
topicSenti <-  read.csv("/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/UsertopicSentiment.csv")
sentiProfile <-  read.csv("/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/users_sentiment_profile.csv")
FreqFeaTe2 <- FreqFeaTe[, c(2,7,12:15)]
motiSTe <- motiTe[, c(2:9)]

#FreqFeaL <- merge(labels, FreqFeaS, by ='user_id', all.y = T)
FreqFeaLT<- merge(FreqFeaTe2, motiSTe, by ='user_id', all.y = T)
FreqFeaLT <- merge(FreqFeaLT, topicSenti, by ='user_id', all.y = T)
#FreqFeaLT <- merge(FreqFeaSTe, sentiProfile)
freqT <- subset(FreqFeaLT, select=-c(family_senti, SWWordCount, X))
freqT <- freqT[2:14]

g.distT <- getGower(freqT, c(4, 5:10))
clustersT <- getMclust(g.distT, 5)
```


merge all the files
```{r }
sentimentProfile <- read.csv('/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/users_sentiment_profile.csv')
FreqFeaTe2<- merge(FreqFeaTe, motiTe, by ='user_id', all.y = T)
FreqFeaTe2 <-  FreqFeaTe2[,c(-2,-16)]  
FreqFeaTe2 <- merge(FreqFeaTe2, topicSenti, by = 'user_id')
FreqFeaTe2$mclust <- clustersT
FreqFeaTe2$X <- NULL
FreqFeaTe2 <- merge(FreqFeaTe2, sentimentProfile, by = 'user_id', all.x=T)

write_csv(FreqFeaTe2, '/Users/lucia/phd_work/Clpsy/suicideDetection/TestFeatures/FreqSentiMotiTopiFea.csv')


```




